\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-28 tex/ms.tex
integrated artist figure

\todo{Make sure to reference Figure~\ref{fig:artist} here.}

@@

@@

% Bibliography
\bibliography{bib}

>>>>

@@

To summarize, we have robustly detected surface features from \TESS 
light curves of Sol d. While the resolution of the map we obtain is limited, 
it is clear that surface features including low-albedo oceanic regions and 
high-albedo cloud banks or land masses are present on this terrestrial 
world. An artist's impression of the planet is shown in Figure~\ref{fig:artist}. 
While somewhat fanciful and rather far-fetched, this artistic interpretation 
is nevertheless broadly consistent with the data.

@@

\newpage
% Bibliography
\bibliography{bib}
